\cvsection{Professional Experience}
\begin{cventries}
  \cventry
  {Google} % Organization
  {UX Research Intern \advisedby{with Dustin Smith, Todd Kulesza, and Sarah D'Angelo}} % Job Title
  {May. - Aug. 2020} % Date(s)
  {Seattle, WA, USA} % Location
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Conducted qualitative research on Go developers' refactoring practices and their engagement with refactoring tools.}
    \end{cvitems}
  }

\cventry
  {Research and Technology Center, Bosch Research} % Organization
  {Research Intern \advisedby{(with \href{https://sites.google.com/view/lisayu/home}{Lisa Yu}, \href{https://sites.google.com/site/wylin1981/}{Wan-Yi Lin}, and \href{https://www.bosch.com/research/know-how/research-experts/alessandro-oltramari-ph-d/}{Alessandro Oltramari})}} % Job Title
  {May. - Aug. 2019} % Date(s)
  {Pittsburgh, PA, USA} % Location
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked on crowd \& AI-powered  projects that aim to improve the safety and performance of autonomous vehicles.}
    \end{cvitems}
  }
\end{cventries}







\cvsection{Research Experience}

\begin{cventries}
\cventry
  {Human-Computer Interaction Institute, Carnegie Mellon University} % Organization
  {Graduate Research Assistant \advisedby{(advised by \href{http://www.cs.cmu.edu/~bam/}{Brad A. Myers} \& \href{http://kittur.org/}{Aniket Kittur})}} % Job Title
  {Aug. 2017 - Present} % Date(s)
  {Pittsburgh, PA, USA} % Location
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Working on \textsc{Unakite}, a system that scaffolds developers in making decisions using information from various web sources and embedding their decision-making structures into their code.}
    \end{cvitems}
  }

\cventry
  {
    \href{https://delphi.cmu.edu/}{Delphi Research Group}, Carnegie Mellon University} % Organization
  {Research Assistant \advisedby{(with \href{http://jodiforlizzi.com/}{Jodi Forlizzi}, \href{http://www.cs.cmu.edu/~roni/}{Roni Rosenfeld} \& \href{http://www.stat.cmu.edu/~ryantibs/}{Ryan Tibshirani})}} % Job Title
  {April. 2020 - Present} % Date(s)
  {Pittsburgh, PA, USA} % Location
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Working on the visualization team of the \href{https://covidcast.cmu.edu/}{COVIDcast system (\underline{https://covidcast.cmu.edu/})}, which displays indicators related to COVID-19 activity level across the U.S. These indicators are derived from a variety of anonymized, aggregated data sources made available by multiple partners, including Facebook, Google, and Quidel. \href{https://www.cmu.edu/news/stories/archives/2020/april/cmu-unveils-covidcast-maps.html}{[\underline{Press coverage}]}}
    \end{cvitems}
  }

\cventry
  {Crowds and Machines Lab, University of Michigan} % Organization
  {Undergraduate Researcher \advisedby{(advised by \href{http://wslasecki.com/}{Walter S. Lasecki})}} % Job Title
  {Mar. 2016 - May. 2017} % Date(s)
  {Ann Arbor, MI, USA} % Location
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked on crowd \& AI-powered interdisciplinary projects that address novel and promising research questions.}
    \end{cvitems}
  }

\cventry
  {Vision \& Learning Lab, University of Michigan} % Organization
  {Research Assistant \advisedby{(advised by \href{http://www.cs.princeton.edu/~jiadeng/}{Jia Deng})}} % Job Title
  {Sept. 2015 - Apr. 2016} % Date(s)
  {Ann Arbor, MI, USA} % Location
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked on a computer vision based toolkit that boosts performance on human-object interaction detection by exploiting human-object spatial relations.}
    \end{cvitems}
  }
\end{cventries}





\cvsection{Teaching Experience}

\begin{cvteachingexps}

  \cvteachingexp
    {Human-Computer Interaction Institute, Carnegie Mellon University} % Organization
    {Teaching Assistant – 05-410/05-610 User-Centered Research \& Evaluation} % Job
    {Fall 2020} % Date(s)
    {
      ~  % Pittsburgh, PA, USA
    } % Location
  
  \cvteachingexp
    {Human-Computer Interaction Institute, Carnegie Mellon University} % Organization
    {Teaching Assistant – \href{https://www.cs.cmu.edu/~bam/uicourse/05631fall2020/}{05-431/05-631 Software Structures for User Interfaces}} % Job
    {Fall 2020} % Date(s)
    {
      ~  % Pittsburgh, PA, USA
    } % Location

  \cvteachingexp
    {Human-Computer Interaction Institute, Carnegie Mellon University} % Organization
    {Teaching Assistant – 05-430/05-630 Programming Usable Interfaces} % Job
    {Fall 2019} % Date(s)
    {
      ~% Pittsburgh, PA, USA
    } % Location
    

  \cvteachingexp
    {University of Michigan, Ann Arbor} % Organization
    {Instructional Aide – \href{https://docs.google.com/document/d/1tn3SMN37z4f_Q8Sey-oe9LuZKh9AMctI7B4HO-zs-F4/edit?usp=sharing}{EECS484 Database Management Systems}} % Job
    {Winter 2017} % Date(s)
    {
      ~% Ann Arbor, MI, USA
    } % Location
    % {
      % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   \item {Prepared and lead weekly discussion sessions and office hours. Prepared teaching materials and course projects. Graded assignments and exams.}
      % \end{cvitems}
    % }
  
  \cvteachingexp
    {University of Michigan, Ann Arbor} % Organization
    {Instructional Aide – \href{http://web.eecs.umich.edu/~aprakash/eecs484/index.html}{EECS484 Database Management Systems}} % Job
    {Fall 2016} % Date(s)
    {
      ~% Ann Arbor, MI, USA
    } % Location
    % {
      % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   \item {Prepared and lead weekly discussion sessions and office hours. Prepared teaching materials and course projects. Graded assignments and exams.}
      % \end{cvitems}
    % }

  \cvteachingexp
    {University of Michigan – Shanghai Jiao Tong University Joint Institute} % Organization
    {Teaching Assistant – Vv255 Multivariate Calculus} % Job
    {Summer 2015} % Date(s)
    {
      ~% Shanghai, China
    } % Location
    % {
      % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   \item {Developed discussion slides and in-class exercises, led weekly discussion sessions, held office hours, graded.}
      % \end{cvitems}
    % }

\end{cvteachingexps}