\cvsection{Selected Honors, Grants, Awards \& Coverage}

\begin{cvhonors}
  \cvhonor
    {\awardtitle{CMU News Coverage on COVIDcast}: \href{https://www.cmu.edu/news/stories/archives/2020/april/cmu-unveils-covidcast-maps.html}{``Carnegie Mellon Unveils Five Interactive COVID-19 Maps''}} % Event
    {Apr. 2020} % Date(s)
  \end{cvhonors}

\begin{cvhonors}
  \cvhonor
    {\awardtitle{Best Paper Honorable Mention Award}, 32nd Annual ACM Symposium on User Interface Software and Technology (UIST 2019)} % Event
    {Oct. 2019} % Date(s)
  \end{cvhonors}

\begin{cvhonors}
  \cvhonor
    {\awardtitle{\href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1814826}{SHF: Small: Knowledge Acceleration for Programming} (\awardamount{\$500,000 over three years)}}, NSF} % Event
    {Jun. 2018} % Date(s)
\end{cvhonors}

\begin{cvhonors}
  \cvhonor
    {\awardtitle{James B. Angell Scholar}, 94th Annual Honors Convocation, University of Michigan} % Event
    {Mar. 2017} % Date(s)
  \end{cvhonors}

\begin{cvhonors}
  \cvhonor
    {\awardtitle{EECS Scholar Award}, 2017 EECS Honors \& Awards Reception, University of Michigan} % Event
    {Mar. 2017} % Date(s)
  \end{cvhonors}

\begin{cvhonors}
  \cvhonor
    {\awardtitle{2016 Summer Undergraduate Research Experience (SURE) program}, University of Michigan} % Event
    {May. 2016} % Date(s)
  \end{cvhonors}

\begin{cvhonors}
  \cvhonor
    {\awardtitle{Tang-Junyuan Fellowship (Top 2/250, \awardamount{\$50,000)}}, UM-SJTU Joint Institute} % Event
    {Jul. 2015, Jul. 2016} % Date(s)
  \end{cvhonors}

\begin{cvhonors}    
  \cvhonor
    {\awardtitle{Dean's List}, University of Michigan} % Event
    {Dec. 2015, Apr. 2016} % Date(s)
  \end{cvhonors}

\begin{cvhonors}
    \cvhonor
    {\awardtitle{Basic Teaching Assistant Certificate}, Center for Learning and Teaching, UM-SJTU Joint Institute} % Event
    {Aug. 2015} % Date(s)
  \end{cvhonors}

\begin{cvhonors}  
  \cvhonor
    {\awardtitle{Dean's List}, UM-SJTU Joint Institute} % Event
    {Dec. 2013, Aug. 2014, Dec. 2014, Aug. 2015} % Date(s)
  \end{cvhonors}

\begin{cvhonors}
  \cvhonor
    {\awardtitle{Fellowship for Outstanding Academic Performance}, Shanghai Jiao Tong University} % Event
    {Jun. 2015} % Date(s)
  \end{cvhonors}
    
\begin{cvhonors}
  \cvhonor
    {\awardtitle{\href{http://www.comap-math.com/mcm/2015Certs/33804.pdf}{Meritorious Winner} (Acceptance: 9\%)}, COMAP Mathematical Contest in Modeling} % Event
    {Apr. 2015} % Date(s)
  \end{cvhonors}


