

\cvsection{Publications}

% conference papers
\cvsubsection{Peer-reviewed Conference Papers}

\begin{cvpubs}
  \cvpub
    {C.3}
    {\faAward}
    {
      \boldPublicationTitle{\href{http://dx.doi.org/10.1145/3332165.3347908}{Unakite: Scaffolding Developers' Decision-Making Using the Web.}}\newline
      \authors{\boldauthor{Michael Xieyang Liu}, Jane Hsieh, Nathan Hahn, Angelina Zhou, Emily Deng, Shaun Burley, Cynthia Taylor, Aniket Kittur, Brad A. Myers.}\newline
      \conference{Proceedings of the 32nd Annual ACM Symposium on User Interface Software and Technology (UIST 2019).}\newline
      \awardDescription{Best Paper Honorable Mention Award.}
    }

  \cvpub
    {C.2}
    {}
    {
      \boldPublicationTitle{\href{https://doi.org/10.1145/3301275.3302305}{Popup: Reconstructing 3D Video Using Particle Filtering to Aggregate Crowd Responses.}}\newline
      \authors{Jean Y. Song, Stephan J. Lemmer, \boldauthor{Michael Xieyang Liu}, Shiyan Yan, Juho Kim, Jason J. Corso, Walter S. Lasecki.}\newline
      \conference{Proceedings of the 24th Annual ACM International Conference on Intelligent UserInterfaces (IUI 2019).}
    }

  \cvpub
    {C.1}
    {}
    {
      \boldPublicationTitle{\href{https://doi.org/10.1109/WACV.2018.00048}{Learning to Detect Human-Object Interactions.}}\newline
      \authors{Yu-Wei Chao, Yunfan Liu, \boldauthor{Xieyang Liu}, Huayi Zeng, Jia Deng.}\newline
      \conference{2018 IEEE Winter Conference on Applications of Computer Vision (WACV 2018).}
    }
\end{cvpubs}




% posters

\cvsubsection{Posters}
\begin{cvpubs}
  \cvpub
    {P.1}
    {}
    {
      \boldPublicationTitle{\href{https://ieeexplore.ieee.org/document/8506517}{An Exploratory Study of Web Foraging to Understand and Support Programming Decisions.}}\newline
      \authors{Jane Hsieh, \boldauthor{Michael Xieyang Liu}, Brad A. Myers, Aniket Kittur.}\newline
      \conference{IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC 2018).}
    }
\end{cvpubs}




% workshop papers
\cvsubsection{Workshop Papers}
\begin{cvpubs}
  \cvpub
    {W.2}
    {}
    {
      \boldPublicationTitle{UNAKITE: Support Developers for Capturing and Persisting Design Rationales When Solving Problems Using Web Resources.}\newline
      \authors{\boldauthor{Michael Xieyang Liu}, Nathan Hahn, Angelina Zhou, Shaun Burley, Emily Deng, Aniket Kittur, Brad A. Myers.}\newline
      \conference{DTSHPS'18 Workshop on Designing Technologies to Support Human Problem Solving, IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC 2018).}
    }

  \cvpub
    {W.1}
    {}
    {
      \boldPublicationTitle{Supporting Knowledge Acceleration for Programming from a Sensemaking Perspective.}\newline
      \authors{\boldauthor{Michael Xieyang Liu}, Shaun Burley, Emily Deng, Angelina Zhou, Aniket Kittur, Brad A. Myers.}\newline
      \conference{Sensemaking Workshop @ CHI Conference on Human Factors in Computing Systems (CHI 2018).}
    }
\end{cvpubs}



